Modeling Intervention Strategies for United States TB Control

### 2014-02-08 in_progress/presentations/paper/draft.tex
Modifying appendix structure

\section{Appendix}
\subsection{Hill Constants}
Below, we detail some of the relevant constants in the Basic Hill Model, and
their best-fit values. A full listing of constants used in the original Hill
Model can be found in <+CITATION HERE+>. 
%\begin{figure}[h]
%  \begin{center}
%    \tiny{
%    \begin{verbatim}
%sigmaLBase  <- 0.057
%fBase       <- 0.187
%transBase   <- 1
%incLTBIBase <- 1
%
%
%#Treatment Effectiveness Data:
%probHosp      <- .49 #Probability of hospitalization for active TB treatment
%efficacyLTBI  <- .9  #LTBI treatement efficacy
%adherenceLTBI <- .64 #LTBI treatment adherence
%probLTBItreatsuccess <- efficacyLTBI*adherenceLTBI 
%
%#Cost Parameter Values: 
%costtb   <- 2985   #TB treatment cost w/o hopsitalization <- Dylan supp. p.11-12
%costhosp <- 25495  #TB treatment cost w/ hospitalization  <- Dylan supp. p.10
%costLTBI <- 403.45 #LTBI treatment cost
%Ct       <- costtb*(1-probHosp) + costhosp*probHosp #Cost of active TB treatment
%Cl       <- costLTBI/probLTBItreatsuccess           #Cost of LTBI treatment
%
%parms <- c(
%mu0   = 1/78,      #Natural mortality rate USB per year
%mu1   = 1/53,      #Natural mortality rate FB per year
%ro    = 0.018,     #USB birth rate per year
%alpha = 0.005,     #FB arrival rate per year
%p     = 0.103,     #Fraction of new infections which are acute (fast
%progressors)
%vF    = 1.5,       #Progression rate of acute infection per year
%l0    = 0.015,     #Prevalence of LTBI in the USB population in 2000
%l1    = 0.211,     #Prevalence of LTBI in the FB population in 2000: 
%r0    = 0.667,     #Fraction of cases due to reactivation in the USB population
%r1    = 0.780,     #Fraction of cases due to reactivation in the FB population
%vL0   = 0.0014,    #Progression rate for reactivation (chronic LTBI) in the USB
%population per year
%vL1   = 0.0010,    #Progression rate for reactivation (chronic LTBI) in the FB
%population per year
%q     = 0.708,     #Fraction of infections progressing to infectious disease
%mud   = 0.115,     #Mortality rate due to TB per year
%x     = 0.111,     #Fraction of re-infected chronic LTBI moving to acute
%infection
%ARI0  = 0.030/100, #Annual risk of infection for USB in 2000
%beta  = 10.39,     #Effective contact rate per year
%e0    = 0.965,     #Fraction of preferred contacts with own population for USB
%e1    = 0.985,     #Fraction of preferred contacts with own population for FB
%g     = 0.0047,    #Fraction of FB arrivals with LTBI who are fast progressors
%phi0  = 1.114,     #Cumulative fraction self-cure and treatment of active
%disease for both populations pre year RATES (USB)
%phi1  = 1.167,     #Cumulative fraction self-cure and treatment of active
%disease for both populations pre year RATES (FB)
%sigmaF0 = 1.296,   #Cumulative fraction of treatment for acute infection for
%both populations per year RATES (USB)
%sigmaF1 = 1.301,   #Cumulative fraction of treatment for acute infection for
%both populations per year RATES (FB)
%sigmaLBase = sigmaLBase, #Treatment rate for chronic LTBI per year
%fBase = fBase,      #Fraction of FB arrivals with LTBI
%
%#2010 New Cases in Population i (millions)
%#source: http://www.cdc.gov/mmwr/preview/mmwrhtml/mm5105a3.htm
%newCases0 = .008714,  #US-born
%newCases1 = .007554,  #Foreign-born
%
%CtBase = Ct,
%ClBase = Cl
%)
%    \end{verbatim}
%  }
%  \end{center}
%  \caption{A list of relevant constants in the Basic \& Extended Hill Model}
%  \label{fig:basicHillConstants}
%\end{figure}
\subsection{The Extended Hill Equations}
Below, we detail the full equations used in the extended hill model. These
equations extend those used in the standard Hill Model. In many cases, the
equations of the Hill model were split into their component parts, which could
then be tracked separately. 
%\begin{figure}[h]
%  \begin{center}
%  \tiny{
%    \begin{verbatim}
%discV   <- 1/(1.03^t)  #amount costs, health states discount constant
%
%#parameter values initialized for each time step
%c01          <- (1-e0)*((1-e1)*N1)/((1-e0)*N0 + (1-e1)*N1)       #proportion of contacts made with FB individuals  (USB)
%c00          <- 1 - c01                                          #proportion of contacts made with USB individuals (USB)
%c10          <- (1-e1)*((1-e0)*N0)/((1-e0)*N0 + (1-e1)*N1)       #proportion of contacts made with USB individuals (FB)
%c11          <- 1 - c10                                          #proportion of contacts made with FB individuals  (FB)
%dLTBIEn      <- f*alpha*(N0+N1)                                  #FB arrivals with LTBI entering
%dnatdeath0   <- mu0 * N0                                         #Natural deaths (USB)
%dnatdeath1   <- mu1 * N1                                         #Natural deaths (FB)
%dtbdeath0    <- mud * (I0 + J0)                                  #TB deaths (USB)
%dtbdeath1    <- mud * (I1 + J1)                                  #TB deaths (FB)
%dtbdeathD0   <- discV * dtbdeath0                                #TB deaths with discounting (USB)
%dtbdeathD1   <- discV * dtbdeath1                                #TB deaths with discounting (FB)
%dprogAcute0  <- vF*F0                                            #Acute LTBI progressions to Active TB disease (USB)
%dprogAcute1  <- vF*F1                                            #Acute LTBI progressions to Active TB disease (FB)
%dprogChron0  <- vL0*L0                                           #Chronic LTBI progressions to Active TB disease (USB)
%dprogChron1  <- vL1*L1                                           #Chronic LTBI progressions to Active TB disease (FB)
%dprogTotal0  <- dprogAcute0 + dprogChron0                        #Progression to Active TB (USB)
%dprogTotal1  <- dprogAcute1 + dprogChron1                        #Progression to Active TB (FB)
%dprogTotalD0 <- discV * dprogTotal0                              #Progression to Active TB with discounting (USB)
%dprogTotalD1 <- discV * dprogTotal1                              #Progression to Active TB with discounting (FB)
%lambda0      <- transmission*(beta*(c00*(I0/N0) + c01*(I1/N1)))  #Forces of Infection (USB)
%lambda1      <- transmission*(beta*(c10*(I0/N0) + c11*(I1/N1)))  #Forces of Infection (FB)
%dexogenous0	 <- x*p*lambda0*L0                                   #Exogenous re-infections of Chronic LTBI to Acute LTBI (USB)
%dexogenous1  <- x*p*lambda1*L1                                   #Exogenous re-infections of Chronic LTBI to Acute LTBI (FB)
%dInterventionCost <- discV * (iCnewCases*1e6*(dprogTotal0+dprogTotal1) + iCtotPop*1e6*(N0+N1) + iCLTBIEn*1e6*dLTBIEn*(1-incLTBI))
%
%#Difference Equations (USB)
%dS0 <- ro*(N0+N1) + sigmaF0*F0 + sigmaL*L0 + phi0*(I0+J0) - lambda0*S0 - mu0*S0
%dF0 <- p*lambda0*S0 + dexogenous0 - (mu0 + vF + sigmaF0)*F0
%dL0 <- (1-p)*lambda0*S0 - dexogenous0 - (mu0 + vL0 + sigmaL)*L0
%dI0 <- q*(dprogAcute0 + dprogChron0) - (mu0 + mud + phi0)*I0
%dJ0 <- (1-q)*(dprogAcute0 + dprogChron0) - (mu0 + mud + phi0)*J0
%
%#Difference Equations (FB)
%dS1 <- (1-incLTBI)*dLTBIEn+(1-f)*alpha*(N0+N1) + sigmaF1*F1 + sigmaL*L1 + phi1*(I1 + J1) - lambda1*S1 - mu1*S1
%dF1 <- g*p*dLTBIEn*incLTBI + p*lambda1*S1 + dexogenous1 - (mu1 + vF + sigmaF1)*F1
%dL1 <- (1-g*p)*dLTBIEn*incLTBI + (1-p)*lambda1*S1 - dexogenous1 - (mu1 + vL1 +sigmaL)*L1
%dI1 <- q*(dprogAcute1 + dprogChron1) - (mu1 + mud + phi1)*I1
%dJ1 <- (1-q)*(dprogAcute1 + dprogChron1) - (mu1 + mud + phi1)*J1
%
%dN0 <- dS0 + dF0 + dL0 + dI0 + dJ0
%dN1 <- dS1 + dF1 + dL1 + dI1 + dJ1
%
%#Cost calculations
%dcL0 <- discV * Cl * sigmaL  * 1e6 * L0                    #cost for Chronic LTBI cures      (USB)
%dcF0 <- discV * Cl * sigmaF0 * 1e6 * F0                    #cost for Acute LTBI cures        (USB)
%dcI0 <- discV * Ct * q*(dprogAcute0 + dprogChron0) * 1e6     #cost for Infectious TB cures     (USB)
%dcJ0 <- discV * Ct * (1-q)*(dprogAcute0 + dprogChron0) * 1e6 #cost for Non-Infectious TB cures (USB)
%dcI0dL0 <- discV * Ct * q*(dprogChron0) * 1e6     #cost for Infectious TB cures     (USB)
%dcI0dF0 <- discV * Ct * q*(dprogChron0) * 1e6     #cost for Infectious TB cures     (USB)
%dcJ0dL0 <- discV * Ct * (1-q)*(dprogAcute0) * 1e6 #cost for Non-Infectious TB cures (USB)
%dcJ0dF0 <- discV * Ct * (1-q)*(dprogAcute0) * 1e6 #cost for Non-Infectious TB cures (USB)
%dcL1 <- discV * Cl * sigmaL  * 1e6 * L1                    #cost for Chronic LTBI cures      (FB)
%dcF1 <- discV * Cl * sigmaF1 * 1e6 * F1                    #cost for Acute LTBI cures        (FB)
%dcI1 <- discV * Ct * q*(dprogAcute1 + dprogChron1) * 1e6     #cost for Infectious TB cures     (FB)
%dcJ1 <- discV * Ct * (1-q)*(dprogAcute1 + dprogChron1) * 1e6 #cost for Non-Infectious TB cures (FB)
%dcI1dL1 <- discV * Ct * q*(dprogChron1) * 1e6     #cost for Infectious TB cures     (USB)
%dcI1dF1 <- discV * Ct * q*(dprogChron1) * 1e6     #cost for Infectious TB cures     (USB)
%dcJ1dL1 <- discV * Ct * (1-q)*(dprogAcute1) * 1e6 #cost for Non-Infectious TB cures (USB)
%dcJ1dF1 <- discV * Ct * (1-q)*(dprogAcute1) * 1e6 #cost for Non-Infectious TB cures (USB)
%dcN0 <- dcF0 + dcL0 + dcI0 + dcJ0                            #Total cost for all treatments (USB)
%dcN1 <- dcF1 + dcL1 + dcI1 + dcJ1                            #Total cost for all treatments (FB)
%    \end{verbatim}
%  }
%  \end{center}
%  \label{fig:extendedHillEqs}
%  \caption{
%    The equations defining the Extended Hill Model, shown in \texttt{R} syntax.
%    In this model, compartments share the same names as they did in the Hill
%    Model, \emph{i.e.} \texttt{S1} is the Foreign Born susceptible population. 
%  }
%\end{figure}
Here, a continuous discounting approximation is used to a discount rate of $3\%$
yearly, found via $discV$. In many of the differential equations, a small $c$ is
used to denote \emph{cost of}. 
\FloatBarrier
\subsection{Estimations for Infectious Rates of FB and USB}

@@

% latex table generated in R 3.0.1 by xtable 1.7-1 package
% Mon Oct 14 00:36:15 2013
\begin{table}
\centering
\begin{tabular}{|r|cccc|} \hline
       & red5    & red10    & red25    & red50    \\ \hline
  2000 & 0.00    & 0.00     & 0.00     & 0.00     \\ 
  2025 & 1115.12 & 2231.70  & 5592.43  & 11227.57 \\ 
  2050 & 3406.41 & 6821.27  & 17117.18 & 34447.71 \\ 
  2075 & 4976.77 & 9967.15  & 25021.33 & 50389.58 \\ 
  2100 & 5942.02 & 11900.90 & 29880.03 & 60189.49 \\ 
   \hline
\end{tabular}
\caption{Cases of TB Averted by Reducing Incoming LTBI by X percent (Cure=\$800)} 
\label{tab:caRed}
\end{table}

% latex table generated in R 3.0.1 by xtable 1.7-1 package
% Mon Oct 14 00:36:15 2013
\begin{table}
\centering
\begin{tabular}{|r|cccc|}
  \hline
 & red5 & red10 & red25 & red50 \\ 
  \hline
2000 & ND & ND & ND & ND \\ 
  2025 & 67908.81 & 67855.46 & 67654.07 & 67332.53 \\ 
  2050 & 28938.23 & 28878.70 & 28699.15 & 28404.13 \\ 
  2075 & 21044.88 & 20989.16 & 20820.53 & 20541.77 \\ 
  2100 & 18130.11 & 18076.11 & 17912.95 & 17642.64 \\ 
   \hline
\end{tabular}
\caption{Cost Per Case Averted by Reducing Incoming LTBI by X percent (in dollar per case, Cure=\$800)} 
\label{tab:cpcaRed}
\end{table}

\subsection{Latin Hypercube Sampling}
The model parameters and variable names referred to in this analysis are listed
below, along with best-fit or estimated values.  Following the example of the
Hill model, we generated a Latin Hypercube Sample varying 18 of the input
parameters.  From these parameters, 16 are identical to the input parameters
varied in the sensitivity analysis of the original Hill model, and the remaining
two parameters, $C_{A}$ and $C_{L}$, are variables for the average cost of
Active and Latent TB treatment in the US.   Probability distributions for the
original 16 parameters of the Hill model were all set to be Triangular, with
mode at the best fit value and end points at the 2.5 and 97.5 percentile values
reported in the Hill model.  Probability distributions for $C_{A}$ and $C_{L}$
were set to be Uniform, with range +/- 10\% of the estimated value.  All
probabilty distributions used to generate the Latin Hypercube are listed in
Table 1.\\

\vspace{5mm}
{\bf Original Hill Model Parameters} 
(USB = US born, FB = Foriegn born)
%\begin{enumerate}[1.] \itemsep 0em
%  \item $\sigma^{L}$ = 0.057 (Treatment rate for chronic LTBI)
%  \item $v^{L}_{0}$  = 0.0014 (Progression rate for reactivation in the USB population)
%  \item $v^{L}_{1}$  = 0.0010 (Progression rate for reactivation in the FB population)
%  \item $f$          = 0.187 (Fraction of FB arrivals with LTBI)
%  \item $p$          = 0.103 (Fraction of new infections which are acute)
%  \item $ARI_{0}$    = 0.00030 (2000 Annual Risk of Infection, USB)
%  \item $q$          = 0.708 (Fraction of infections progressing to infectious disease)
%  \item $g$          = 0.0047 (Fraction of FB arrivals with LTBI who are fast progressors)
%  \item $\sigma^{F}$ = 0.461 (Cumulative fraction of treatment for acute infection)
%  \item $r_{0}$      = 0.667 (Fraction of cases due to reactivation in USB population)
%  \item $r_{1}$      = 0.780 (Fraction of cases due to reactivation in FB population)
%  \item $\mu^{d}$    = 0.115 (Mortality rate due to TB)
%  \item $x$          = 0.111 (Fraction of re-infected chronic LTBI moving to acute infection)
%  \item $\phi$       = 0.897 (Cumulative fraction self-cure and treatment of active disease)
%  \item $e_{0}$      = 0.965 (Fraction of preferred contacts within own population for USB)
%  \item $e_{1}$      = 0.985 (Fraction of preferred contacts within own population for FB)
%\end{enumerate}
%\vspace{2mm}
\begin{align*}
  \sigma^{L} &= 0.057   &&\text{(Treatment rate for chronic LTBI)}\\
  v^{L}_{0}  &= 0.0014  &&\text{(Progression rate for reactivation in the USB
                                 population)}\\
  v^{L}_{1}  &= 0.0010  &&\text{(Progression rate for reactivation in the FB
                                 population)}\\
  f          &= 0.187   &&\text{(Fraction of FB arrivals with LTBI)}\\
  p          &= 0.103   &&\text{(Fraction of new infections which are acute)}\\
  ARI_{0}    &= 0.00030 &&\text{(2000 Annual Risk of Infection, USB)}\\
  q          &= 0.708   &&\text{(Fraction of infections progressing to infectious
                                 disease)}\\
  g          &= 0.0047  &&\text{(Fraction of FB arrivals with LTBI who are fast
                                 progressors)}\\
  \sigma^{F} &= 0.461   &&\text{(Cumulative fraction of treatment for acute
                                 infection)}\\
  r_{0}      &= 0.667   &&\text{(Fraction of cases due to reactivation in USB
                                 population)}\\
  r_{1}      &= 0.780   &&\text{(Fraction of cases due to reactivation in FB
                                 population)}\\
  \mu^{d}    &= 0.115   &&\text{(Mortality rate due to TB)}\\
  x          &= 0.111   &&\text{(Fraction of re-infected chronic LTBI moving to
                                 acute infection)}\\
  \phi       &= 0.897   &&\text{(Cumulative fraction self-cure and treatment of
                                 active disease)}\\
  e_{0}      &= 0.965   &&\text{(Fraction of preferred contacts within own
                                 population for USB)}\\
  e_{1}      &= 0.985   &&\text{(Fraction of preferred contacts within own
                                population for FB)}\\
%\end{align*}
&\text{\bf Additional Cost Parameters}\\
%\begin{align*}
  C_{A} &= \$14,014.50 &&\text{(Cost per Active TB treatment)}\\
  C_{L} &= \$700       &&\text{(Cost per Latent TB treatment)}
\end{align*}
%\begin{enumerate}[1.] \itemsep 0em
%  \item $C_{A}$ = \$14,014.50 (Cost per Active TB treatment)
%  \item $C_{L}$ = \$700 (Cost per Latent TB treatment)
%\end{enumerate}
\vspace{5mm}

>>>>

\section{Appendix}
\subsection{Hill Constants}
Below, we detail some of the relevant constants in the Basic Hill Model, and
their best-fit values. A full listing of constants used in the original Hill
Model can be found in <+CITATION HERE+>. \\
\textit{(USB = US born, FB = Foriegn born)}
\begin{align*}
  \sigma^{L} &= 0.057   &&\text{(Treatment rate for chronic LTBI)}\\
  v^{L}_{0}  &= 0.0014  &&\text{(Progression rate for reactivation in the USB
                                 population)}\\
  v^{L}_{1}  &= 0.0010  &&\text{(Progression rate for reactivation in the FB
                                 population)}\\
  f          &= 0.187   &&\text{(Fraction of FB arrivals with LTBI)}\\
  p          &= 0.103   &&\text{(Fraction of new infections which are acute)}\\
  ARI_{0}    &= 0.00030 &&\text{(2000 Annual Risk of Infection, USB)}\\
  q          &= 0.708   &&\text{(Fraction of infections progressing to infectious
                                 disease)}\\
  g          &= 0.0047  &&\text{(Fraction of FB arrivals with LTBI who are fast
                                 progressors)}\\
  \sigma^{F} &= 0.461   &&\text{(Cumulative fraction of treatment for acute
                                 infection)}\\
  r_{0}      &= 0.667   &&\text{(Fraction of cases due to reactivation in USB
                                 population)}\\
  r_{1}      &= 0.780   &&\text{(Fraction of cases due to reactivation in FB
                                 population)}\\
  \mu^{d}    &= 0.115   &&\text{(Mortality rate due to TB)}\\
  x          &= 0.111   &&\text{(Fraction of re-infected chronic LTBI moving to
                                 acute infection)}\\
  \phi       &= 0.897   &&\text{(Cumulative fraction self-cure and treatment of
                                 active disease)}\\
  e_{0}      &= 0.965   &&\text{(Fraction of preferred contacts within own
                                 population for USB)}\\
  e_{1}      &= 0.985   &&\text{(Fraction of preferred contacts within own
                                population for FB)}\\
\end{align*}
\subsection{The Extended Hill Equations}
Below, we detail some of the relevant equations used in the extended hill model.
In many cases, the equations of the Hill model were split into their component
parts, which could then be tracked separately.

{\huge \color{red} TODO: What equations should be put in here?}

Here, a continuous discounting approximation is used to a discount rate of $3\%$
yearly, found via $discV$. In many of the differential equations, a small $c$ is
used to denote \emph{cost of}. 
\FloatBarrier
\subsection{Estimations for Infectious Rates of FB and USB}

@@

% latex table generated in R 3.0.1 by xtable 1.7-1 package
% Mon Oct 14 00:36:15 2013
\begin{table}
\centering
\begin{tabular}{|r|cccc|} \hline
       & red5    & red10    & red25    & red50    \\ \hline
  2000 & 0.00    & 0.00     & 0.00     & 0.00     \\ 
  2025 & 1115.12 & 2231.70  & 5592.43  & 11227.57 \\ 
  2050 & 3406.41 & 6821.27  & 17117.18 & 34447.71 \\ 
  2075 & 4976.77 & 9967.15  & 25021.33 & 50389.58 \\ 
  2100 & 5942.02 & 11900.90 & 29880.03 & 60189.49 \\ 
   \hline
\end{tabular}
\caption{Cases of TB Averted by Reducing Incoming LTBI by various percentages
         (Cure=\$800)} 
\label{tab:caRed}
\end{table}

% latex table generated in R 3.0.1 by xtable 1.7-1 package
% Mon Oct 14 00:36:15 2013
\begin{table}
\centering
\begin{tabular}{|r|cccc|} \hline
       & red5     & red10    & red25    & red50    \\ \hline
  2000 & ND       & ND       & ND       & ND       \\ 
  2025 & 67908.81 & 67855.46 & 67654.07 & 67332.53 \\ 
  2050 & 28938.23 & 28878.70 & 28699.15 & 28404.13 \\ 
  2075 & 21044.88 & 20989.16 & 20820.53 & 20541.77 \\ 
  2100 & 18130.11 & 18076.11 & 17912.95 & 17642.64 \\ \hline
\end{tabular}
\caption{Cost Per Case Averted by Reducing Incoming LTBI by various percent (in
dollars per case, Cure=\$800)} 
\label{tab:cpcaRed}
\end{table}

\subsection{Latin Hypercube Sampling}
%The model parameters and variable names referred to in this analysis are listed
%below, along with best-fit or estimated values. 
Following the example of the
Hill model, we generated a Latin Hypercube Sample varying 18 of the input
parameters.  From these parameters, 16 are identical to the input parameters
varied in the sensitivity analysis of the original Hill model, and the remaining
two parameters, $C_{A}$ and $C_{L}$, detailed below, are variables for the average cost of
Active and Latent TB treatment in the US.   Probability distributions for the
original 16 parameters of the Hill model were all set to be Triangular, with
mode at the best fit value and end points at the 2.5 and 97.5 percentile values
reported in the Hill model.  Probability distributions for $C_{A}$ and $C_{L}$
were set to be Uniform, with range +/- 10\% of the estimated value.  All
probabilty distributions used to generate the Latin Hypercube are listed in
Table 1.\\

{\bf Additional Cost Parameters}
\begin{align*}
  C_{A} &= \$14,014.50 &&\text{(Cost per Active TB treatment)}\\
  C_{L} &= \$700       &&\text{(Cost per Latent TB treatment)}
\end{align*}
\vspace{5mm}
